Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-07-23 automatica/paper.tex
paper

\begin{theorem}
  \label{th:safety}
\rev{Assuming that the initial set is included within the safe set, }
if a controller is safe for each of the corner cases of the hyper-box of allowed initial states, 
i.e., the vertex states, then it is safe for any initial state in the hyper-box. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we note is convex since it is a hyper-box. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\rev{Recall that we have assumed that the initial set lies within the safe set, and that both are (convex) hyper-boxes. The conclusion follows. }
\qed
\end{proof}
Summarising, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables). \todo{Add remark from reviewer that this number can be lower in actuality?}

>>>>

\begin{theorem}
  \label{th:safety}
\rev{Assuming that the initial set is included within the safe set, }
if a controller is safe for each of the corner cases of the hyper-box of allowed initial states, 
i.e., the vertex states, then it is safe for any initial state in the hyper-box. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we note is convex since it is a hyper-box. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\rev{Recall that we have assumed that the initial set lies within the safe set, and that both are (convex) hyper-boxes. The conclusion follows. }
\qed
\end{proof}
Summarising, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables). 
%\todo{Add remark from reviewer that this number can be lower in actuality?} 
\rev{Whilst this full check on all vertices might not be necessary in general  
(it might be simplified in special cases or under special conditions), 
it does not represent the bottleneck of our overall method, so we can
safely rely on its current form. }
